Learning CNN filters from user-drawn image \changed{markers} for coconut-tree image classification

### 2020-08-19 main.tex
fix some references

\documentclass[journal, twoside]{IEEEtran}

@@

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

\author{Italos~Estilon~de~Souza,~
and~Alexandre~Xavier~Falc\~{a}o,~\IEEEmembership{Member,~IEEE}}

\markboth{IEEE GEOSCIENCE AND REMOTE SENSING LETTERS,~Vol.~17, No.~11, November~2020}%
{de Souza \MakeLowercase{\textit{et al.}}: Learning CNN filters from user-drawn image makers for coconut-tree image classification}

>>>>

\documentclass[journal, twoside, final]{IEEEtran}

@@

@@

\author{Italos~Estilon~de~Souza,~and~Alexandre~Xavier~Falc\~{a}o,~\IEEEmembership{Member,~IEEE}}

\markboth{IEEE GEOSCIENCE AND REMOTE SENSING LETTERS,~Vol.~17, No.~11, November~2020}%
{de Souza and Falc\~{a}o: Learning CNN filters from user-drawn image markers}
